\documentclass[11pt]{article}
%\usepackage[showframe]{geometry}
\usepackage[top=.7in, bottom=.8in, left=1.3in, right=1.3in]{geometry}
\usepackage{lastpage}
\usepackage{nopageno}
\usepackage{fancyhdr}
\usepackage{enumitem}
\usepackage{verbatim}
\usepackage{titlesec}
\usepackage{setspace}
\setlist[itemize]{noitemsep, topsep=10pt}
\usepackage[usenames,dvipsnames,svgnames]{xcolor}
\definecolor{RyanRed}{RGB}{44,65,109}
\titlespacing*{\subsection}{0pt}{*1}{*.2}
\titlespacing*{\section}{0pt}{*1.5}{*1}
\usepackage{multicol}
\frenchspacing
\renewcommand{\familydefault}{\sfdefault}
\cfoot{\thepage\ of \pageref{LastPage} }
\setlength\multicolsep{0pt}
\setcounter{secnumdepth}{0}
\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	filecolor=magenta,
	urlcolor=RoyalBlue,
}
\begin{document}

	\noindent \textbf{{\fontsize{38pt}{\parskip}\selectfont \color{RyanRed} Ryan Kresse}}
	\smallskip

	\noindent {\fontsize{10pt}{\parskip}\selectfont rkresse53@gmail.com $\vert$ ryankresse.com $\vert$ github.com/ryankresse $\vert$ 843-696-8459}

	\section{Summary}
	Data professional with experience in both data science and data engineering. Knowledgeable in statistics, machine learning, Python, SQL and Apache Spark. Life-long learner and passionate about problem solving with analytics.
	\section{Technical Skills}
		\begin{multicols}{4}
				\begin{itemize}
				\item Statistics/ML
				\item Scikit-learn
				\item Java

				\columnbreak
				\item Python
				\item Pytorch
				\item Spark

				\columnbreak
				\item Sql
				\item Numpy
				\item Hive/Impala

				\columnbreak
				\item Pandas
				\item Unix
				\item Git
				\columnbreak

			\end{itemize}
		\end{multicols}



	\section{Experience}

	\subsection{\normalsize{Data Scientist, Data Engineer and Team Lead, Allstate}}
	{\fontsize{10pt}{\parskip}\selectfont Charlottesville, VA 2021--}

	\smallskip

	\noindent
	I've worn a number of hats at Allstate -- application developer, data engineer and data scientist. From 2018 to early 2021,
	I was a member and lead of the ATSV Data Science team, working on a variety of projects, including building graph models to detect fraud,
	using stats to prioritize cybersecurity risks, and creating forecasts and analyses to set hiring goals and understand employee attrition.
	\medskip

	\noindent
	In early 2021, our team was called on to help bootstrap the D\&IS Fraud Technology team,
	for which I'm the data engineering team lead. We have built data pipelines and dashboards to generate and monitor fraud risk scores, and we've created a web application
	to gather feedback on potential fraud from investigators.


\subsection{\normalsize{Applications Developer, Highmark Health}}
		{\fontsize{10pt}{\parskip}\selectfont Pittsburgh, PA, 2015--2018}

		\smallskip

		\noindent
	  I joined a complex, multi-year project mid-development, and when the senior developers left, I stepped up and guided the UI team the rest of the way
		to the app's successful release. I also served as a mentor, teaching and onboarding new UI developers on our team and coaching other teams
		in the organization.


\subsection{\normalsize{Writer, Moosylvania Marketing}}
	{\fontsize{10pt}{\parskip}\selectfont St. Louis, MO, 2012--2015}

	\smallskip

	\noindent
	In my first career, I worked as a writer at an advertising agency, creating campaigns for clients like PayPal, Enterprise Rent-A-Car, Capital One and Drambuie.

	\section{Education}
		\begin{itemize}
      \item Emory University, BA, 2009
			\item University of Missouri, MA, 2012
		  \item Data Science Courses:
				\begin{itemize}[noitemsep,nolistsep]
						\item Coursera Machine Learning
						\item Harvard CS109 Data Science
						\item Coursera Statistics With R
						\item Stanford CS231 Convolutional Neural Networks
						\item Fastai Courses
						\item Stanford CS224N NLP with Deep Neural Networks
				\end{itemize}

		\end{itemize}
\end{document}
