\documentclass[10pt]{article}
%\usepackage[showframe]{geometry}
\usepackage{geometry}

\usepackage{nopageno}
\usepackage{enumitem}
\usepackage{verbatim}
\usepackage{multicol}
\frenchspacing
\setcounter{secnumdepth}{0}
\begin{document}
	%\title{Ryan Kresse}
	%\date{}
	%\maketitle
	\begin{flushleft}
		{\Huge Ryan Kresse}
	\end{flushleft}	%rkresse53@gmail.com - ryankresse.com - github.com/ryankresse
	
	
	\begin{comment}
		\renewcommand{\abstractname}{Summary}
	
		\begin{abstract}
			Frontend developer with experience building complex, single page Angular applications. Life-long student particularly passionate about data, statistics and machine learning. Craftsman excited by building things well and solving difficult
		problems.
		\end{abstract}
	\end{comment}
	\section{Summary}
		Frontend developer with experience building complex, single page Angular applications. Life-long student particularly passionate about data, statistics and machine learning. Craftsman excited by building things well and solving difficult
		problems.
	
	\section{Technical Skills}
		\begin{multicols}{4}
			\begin{itemize}[noitemsep]
				\item Javascript 
				\item Angular 
				\item HTML 
				\item CSS 
				\item Karma 
				\item Jasmine 
				\columnbreak 
				
				\item Gulp 
				\item Webpack
				\item Sass
				\item Node 
				\item Npm 
				\item Python 
				\columnbreak 
				
				\item Numpy 
				\item Scikit-learn 
				\item Tensorflow 
				\item Pandas 
				\item Matplotlib
				\item Seaborn 
				\columnbreak
				
				\item Sql 
				\item Unix 
				\item AWS 
				\item PySpark
			\end{itemize}
		\end{multicols}
		
	\section{Experience}
		\subsection{\normalsize{Senior Application Developer, Highmark Health, Pittsburgh, PA, July 2015--}}
		\begin{itemize}[noitemsep]
		\item Build dynamic, single page applications with Javascript (Angular), HTML and CSS
		\item Major contributor to the release of an app that will save company ~650K annually
		\item Joined a multi-year project in the middle of development and quickly learned the large and complex codebase, becoming the lead UI developer and guiding the UI team to the application's successful release
		\item Teach new UI developers, helping them become successful contributors to the team
		\item Advise and coach other teams as they get their new Angular projects off the ground
		\item Write clean code, as well as unit tests to ensure correctness and prevent regressions
		\end{itemize}
		
	\subsection{\normalsize{Writer, Moosylvania Marketing, St. Louis, MO, Aug. 2012-- Apr. 2015}}
	\begin{itemize}[noitemsep]
		\item Lead writer on PayPal, helping grow it from a small account into agency’s most important and profitable client
		\item Other clients included Enterprise Rent-A-Car, Capital One and Drambuie
	\end{itemize}
	
	\section{Education}
		\begin{itemize}[noitemsep]
			\item University of Missouri, M.A Strategic Communication, May 2012
			\item Emory University, B.A Anthropology and Music, June 2009
			\item Self-study:
				\begin{itemize}[noitemsep]
						\item Coursera: Machine Learning 
						\item Harvard CS109: Data Science
						\item Coursera: Statistics With R 
						\item Stanford CS231: Convolutional Neural Networks
						\item Practical Deep Learning For Coders 
						\item Stanford CS224N: NLP with Deep Neural Networks
				\end{itemize}
					
				
		\end{itemize}
		
			
\end{document}
